---
title: "Mathur_Johri_Jakobs_Pourhamidi_Final_Project"
author: "Abeer Mathur, Marvin Jakobs, Divyesh Johri, Cinah Pourhamidi"
date: "2022-12-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyverse)
library(readr)
library(rpart)
```

#### Load and clean datasets
```{r message=FALSE, warning=FALSE}
CODGameModes <- read.csv("https://raw.githubusercontent.com/Abeermathur7/STAT380Final/main/CODGameModes.csv")
CODGames_p1_380 <- read.csv("https://raw.githubusercontent.com/Abeermathur7/STAT380Final/main/CODGames_p1_380.csv")
CODGames_p2_380 <- read.csv("https://raw.githubusercontent.com/Abeermathur7/STAT380Final/main/CODGames_p2_380.csv")

CODGames<- rbind(CODGames_p1_380,CODGames_p2_380) #combine raw data

dupModes <- CODGameModes
dupModes$Mode <- paste("HC -", dupModes$Mode) #adding HC mode limits
allModes <- rbind(dupModes,CODGameModes)
```

### Task 1 (Exploratory Analysis): 

#### Research Question: Which game mode is most likely to reach the score limit? 
```{r message=FALSE, warning=FALSE}
scoreLimit <- left_join(CODGames,allModes, by = c("GameType"="Mode")) #add score limit column

scoreLimit <- tidyr::separate(data = scoreLimit, col = Result, sep = "-", into = c("score1","score2")) #put each team score into individual columns

scoreLimit <- mutate(scoreLimit, limitReached = ifelse(score1 == ScoreLimit | score2 == ScoreLimit,1,0)) #note if either team reached the limit
         
limitList <- scoreLimit %>% group_by(GameType) %>% tally(limitReached) #group by and count games that reached score limit for each mode
totalCount <- scoreLimit %>% group_by(GameType) %>% summarise(count = n()) #total games of each mode played
limitList$total <- totalCount$count 
limitList <- mutate(limitList, limitProb = n/total) #find ratio of score limit reached to games played
limitList %>% arrange(desc(limitProb)) #print descending
```
```{r}
ggplot(limitList, aes(x=GameType,y=limitProb)) + 
  geom_bar(stat = "identity", fill = "#301934") + 
  theme(axis.text.x=element_text(angle=45, hjust=1)) +
  ylab("Prob of Score Limit Reached")
```

Both types of Domination and Hardpoint have the highest chances of reaching the score limit, with domination reaching it 100% of the time. This may be because...............

### Task 2 (Inference):

#### Research Question: Which predictors are associated with the TotalXP?
```{r}
subCODGames <- CODGames %>% select(1:16) #remove cols where almost every row is NA
model <- rpart(TotalXP ~ ., data = subCODGames) #build rpart model
sig <- as_tibble(model$frame$var) #leafs and splits from rpart frame to tibble
sig_predictors <- sig %>% filter(. != "<leaf>") %>% unique() #delete duplicate splits & all leafs for sig vars

sig_predictors
```

XPType, Result, Eliminations, Date, and Map1 are the predictors that are most associated with TotalXP. We calculated this by preforming an rpart on TotalXP and picked out the variables that were used to split the data to record them as significant predictors.

#### Research Question: Of the predictors associated with the response, select one of the predictors and explain the relationship between the predictor and TotalXP. 
```{r message=FALSE, warning=FALSE}
groupElim <- CODGames %>% group_by(Eliminations) %>% summarize(avgXP = mean(TotalXP)) #group by num of eliminations and average the TotalXP
elim.reg <- lm(avgXP ~ Eliminations, data = groupElim) #create the lm to report the slope/intercept later
string <- paste("XP =",round(elim.reg$coefficients[[2]],2),"Elims +",round(elim.reg$coefficients[[1]],2)) #turn lm coeff into a formula string
ggplot(groupElim, aes(x=Eliminations, y=avgXP)) + geom_point() +  #ggplot with method lm and the formula string created above
  geom_smooth(method = "lm") + annotate("text",x = 10, y = 40000, label = string,size = 4) 
```

The predictor 'Eliminations' has a very strong positive linear correlation to the TotalXP variable. We calculated this by grouping the number of eliminations into a new dataframe and averaging the TotalXP received by people getting that number of eliminations into a new column of that dataframe. We then ggplotted it and observed a very strong linear relationship before adding the blue line and creating a linear model with the two variables to print its slope and intercept.
